Constraining tensorial and scalar couplings with $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-03-26 tensor/draft/draft-tensor-op.tex
[draft-tensor-op] added new prior average of BZ and KMPW LCSR results for plus and tensor FF and text rephrasinng

\begin{abstract}
  The angular distribution of $B\to K\bar\ell\ell$ ($\ell = e,\,\mu,\,\tau$)
  provides a lepton-forward-backward asymmetry $A_{\rm FB}^\ell$ and a flat
  term $F_H^\ell$ that are both suppressed in the standard model and very
  sensitive to nonstandard tensorial and scalar contributions. We use latest
  experimental results for $\ell = \mu$ in combination with $B_s\to \bar\mu\mu$
  to derive stronger model-independent constraints on tensorial and scalar
  effective couplings and determine their impact on $B\to K^*\bar\mu\mu$
  angular observables. Most notably, the measurement of $F_H^\mu$ provides
  constraints on (pseudo-)scalar couplings and their chirality-flipped
  counterparts that are complementary to the once from the branching ratio
  $B_s\to \bar\mu\mu$, which allows to put for the first time upper bounds
  on all four couplings.
\end{abstract}

@@

Both observables exhibit strong suppression factors for vectorial and dipole
couplings present in the SM, thereby enhancing their sensitivity to tensorial and
scalar couplings \cite{Bobeth:2007dw, Bobeth:2012vn}. A similar enhancement of
scalar couplings compared to helicity-suppressed vectorial couplings of the SM
is well-known from $B_s\to \bar\mu\mu$. Unfortunately the limited data set of
$B\to K^*(\to K\pi) \bar\ell\ell$ from LHCb \cite{Aaij:2013qta} still does not
allow to perform current angular analysis without the assumption of vanishing
scalar and tensorial couplings in this decay mode. In the future also certain
angular observables in $B\to K^* \bar\ell\ell$ will provide additional constraints
on such couplings, as for example $J_{6c}$ \cite{Altmannshofer:2008dz}
and the linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
\cite{Matias:2012xw, Bobeth:2012vn} as well as at low recoil the experimental
test of the relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 = 0$~\cite{Bobeth:2012vn}.

Here we exploit current data from $B^+\to K^+ \bar\mu\mu$ and $B_s\to \bar\mu\mu$
to derive stronger constraints then before on tensorial and scalar couplings in
various model-independent scenarios and study their impact on the yet not
measured analogous observables in $B\to K^* \bar\ell\ell$. In \refsec{sec:EFT},
we specify the effective theory of $|\Delta B| = 1$ decays, on which our
model-independent fits are based on. We discuss the dependence of observables
in $B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$ on the tensorial and scalar
couplings in \refsec{sec:observables} and specify also the experimental input
used in the fits. The constraints on tensorial and scalar couplings from the data
are presented for several model-independent scenarios in \refsec{sec:results}.
Technical details on the treatment of theory uncertainties are relegated to
appendices.

@@

In the framework of the $|\Delta B| = |\Delta S| = 1$ effective theory
\begin{align}
  \label{eq:Heff}
  {\cal L}_{\rm eff} & =
   \frac{4 G_F}{\sqrt{2}} \,\frac{\alE}{4 \pi}\, V_{tb}^{} V_{ts}^\ast
       \sum_{\ell = e, \mu,\tau} \sum_i  \wilson[\ell]{i}(\mu_b)  \Op_i + \text{h.c.}
\end{align}
the most general dimension-six flavor-changing operators $\Op_i$ mediating
$b\to s \bar\ell\ell$ are classified according to their chiral structure.
There are dipole ($i = 7,7')$ and vectorial ($i = 9,9',10,10'$) operators
\begin{equation}
  \label{eq:SM:ops}
\begin{aligned}
  \Op_{7(7')} &
  = \frac{m_b}{e}\!\[\bar{s} \sigma^{\mu\nu} P_{R(L)} b\] F_{\mu\nu}\,,
\\
  \Op_{9(9')} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \ell\]\,,
\\[0.1cm]
  \Op_{10(10')} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
further scalar ($i = S,S',P,P'$) operators
\begin{equation}
  \label{eq:scalar:ops}
\begin{aligned}
  \Op_{S(S')} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \ell\]\,,
\\[0.1cm]
  \Op_{P(P')} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
and tensor ($i = T,T5$) operators
\begin{equation}
  \label{eq:tensor:ops}
\begin{aligned}
  \Op_{T} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \ell\]\,,
\\[0.1cm]
  \Op_{T5} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
where the notation $\Op_{T5} = i/2\, \varepsilon^{\mu\nu\alpha\beta}
\[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma_{\alpha\beta} \ell\]$ is
also used frequently in the literature. Their respective short-distance couplings,
the Wilson coefficients $\wilson[\ell]{i}(\mu_b)$ are evaluated at the typical
scale of the $b$-quark mass $\mu_b \sim m_b$ and can be modified from SM predictions
in the presence of new physics.

The SM values $\wilson[\ell]{7,9,10}$ are obtained at NNLO \cite{Bobeth:2003at,
Huber:2005ig} and depend on the fundamental parameters of the top-quark and
$W$-boson masses, as well as on the sine of the weak mixing angle. Moreover,
they are universal for the three lepton flavors $\ell = e,\, \mu,\, \tau$.
All other Wilson coefficients are numerically suppressed or zero:
$\wilson[SM]{7'} = m_s/m_b\, \wilson[SM]{7}$, $\wilson[SM]{S,S',P,P'} \sim
{\cal O}(m_b^2/m_W^2)$, and $\wilson[SM]{9',10',T,T5} = 0$. Beyond the SM,
lepton-flavor non-universal effects are possible in principle and have been
discussed for example recently \cite{Alonso:2014csa, Hiller:2014yaa, Ghosh:2014awa,
Biswas:2014gga, Hurth:2014vma, Glashow:2014iga, Altmannshofer:2014rta, Hiller:2014abc} in
connection with the measurement of $R_K = {\cal B}_\mu/{\cal B}_e$ in
$q^2 \in [1, 6]$ GeV$^2$ \cite{Aaij:2014ora}, which deviates by $2.6\sigma$
from the SM prediction $R_K^{\rm SM} = 1.00$ \cite{Bobeth:2007dw, Bouchard:2013mia}.

@@

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensorial and scalar
couplings has been presented in \cite{Bobeth:2007dw, Bobeth:2012vn}, adopting
the effective theory \refeq{eq:Heff}, i.e. neglecting higher dimensional operators
with $\mbox{dim} > 6$. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2)|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}\,, &
  A_{\rm FB}^\ell|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests.
The $F_H^\ell(q^2)|_{\rm SM}$
is strongly suppressed away from both kinematical endpoints in $q^2$,
except for $\ell = \tau$, \cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.
Non-zero values
of $A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher order QED corrections,
which in principle could also give additional $\cos\theta_\ell$ dependence
to the angular distribution~\refeq{eq:ang-distr}, however, currently there is
no solid estimate available for this source of SM background.

@@

There are also angular observables $J_i$ in $B\to K^*(\to K\pi)\,
\bar\ell\ell$ with the same properties, i.e. tensorial and scalar contributions
are kinematically enhanced by a factor $\sqrt{q^2}/m_\ell$ over vectorial once
present in the SM or their respective interference terms. These are $J_{6c}$
and the two linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
with explicit formulas given in \refapp{app:BKstarellell}.
In the limit of vanishing lepton mass one obtains that
\begin{align}
  J_{6c} & \propto
    \mbox{Re}\big[(\wilson[]{P} - \wilson[]{P'})\, \wilson[\ast]{T}
                - (\wilson[]{S} - \wilson[]{S'})\, \wilson[\ast]{T5}\big]
\intertext{is sensitive to the interference of tensorial and scalar operators,
  complementary to lepton forward-backward asymmetry of $B\to K \bar\ell\ell$}
  \label{eq:AFB-dependence}
  A_{\rm FB}^\ell & \propto
    \mbox{Re}\big[(\wilson[]{P} + \wilson[]{P'})\, \wilson[\ast]{T5}
                + (\wilson[]{S} + \wilson[]{S'})\, \wilson[\ast]{T}\big]
                \Big/ \Gamma_\ell \,,
\end{align}
i.e., with an interchange of tensorial contributions $T \leftrightarrow T5$.
We note also that $J_{6c}$ contributes to lepton forward-backward asymmetry
of $B\to K^* \bar\ell\ell$ being $\propto (J_{6s} + J_{6c}/2)$. Since
it has to compete with $J_{6s}$ in this observable, a separate measurement of
$J_{6s}$ and $J_{6c}$ is necessary. Further, only tensorial contributions enter
\begin{align}
  (J_{1s} - 3\, J_{2s}) & \propto
  \left(\ldots |\wilson{T}|^2 + \ldots |\wilson{T5}|^2 \right) \,,
\end{align}
where the dots indicate different kinematical and form factor dependences.
On the other hand, tensorial and scalar contributions enter
\begin{equation}
\begin{aligned}
  (J_{1c} + J_{2c}) & \propto
      \ldots \left(|\wilson{T}|^2 + |\wilson{T5}|^2 \right)
\\
  & + \ldots \left(|\wilson{S} - \wilson{S'}|^2 + |\wilson{P} - \wilson{P'}|^2 \right) \,,
\end{aligned}
\end{equation}
which is similar to the dependence of $F_H^\ell$ in $B\to K
\bar\ell\ell$
\begin{equation}
  \label{eq:FH-dependence}
\begin{aligned}
  F_H^\ell  \propto & \Big[
      \ldots \left(|\wilson{T}|^2 + |\wilson{T5}|^2\right)
\\
  & + \ldots \left(|\wilson{S} + \wilson{S'}|^2 + |\wilson{P} + \wilson{P'}|^2 \right)
  \Big]
  \Big/ \Gamma_\ell \,.
\end{aligned}
\end{equation}
Concerning $F_H^\ell$, the involved kinematical factors --- see \cite{Bobeth:2007dw,
Bobeth:2012vn} --- are such that tensorial and scalar couplings contribute only
constructively, apart of cancellations among $\wilson{S(P)}$ and $\wilson{S'(P')}$.
Further, interference terms (in the numerator of $F_H^\ell$) of $(\wilson{T} \times
\wilson{7,7',9,9'})$ and $(\wilson{P,P'} \times \wilson{10,10'})$ are suppressed
by $m_\ell/\sqrt{q^2}$, but can become relevant in case $\wilson{T} \ll \wilson{7,7',9,9'}$
and $\wilson{P,P'} \ll\wilson{10,10'}$ can overcome this suppression factor,
respectively.

The observables $F_H^\ell$ \refeq{eq:FH-dependence} and $A_{\rm FB}^\ell$
\refeq{eq:AFB-dependence} are measured in the angular
distribution \refeq{eq:ang-distr} of $B\to K \bar\ell\ell$ being normalised to the
decay width $\Gamma_\ell$, whereas $J_{6c}$,  $(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$
appear in the unnormalised angular distribution of $B\to K^* \bar\ell\ell$.
Hence in the former, uncertainties due to form factors can cancel in part
\cite{Bobeth:2007dw, Bobeth:2012vn}. So-called ``optimised'' versions $S_1$, $M_1$ and
$M_2$ for the low-$q^2$ region have been identified in~\cite{Matias:2012xw}
for $J_{6c}$,  $(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$, respectively.
In \refapp{app:BKstarellell} potential normalisations are discussed that
could serve to form optimised observables at high $q^2$ for special cases of
either vanishing chirality-flipped vectorial or tensorial or scalar couplings.
In the most general case, however, there are no optimised observables.
Although form factors do not cancel in this case, it might be
still advantageous to use normalisations, for example when the overall
normalisation of $B\to K^*$ form factors constitutes a major theoretical
uncertainty.

\begin{table*}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lccc}
\hline
Channel & Constraints & Kinematics & Source
\\
\hline \hline
$B_s\to \bar\mu\mu$
& $\int\dd\tau \BR(\tau)$ &  --  & \cite{Aaij:2013aka,Chatrchyan:2013bka,CMS:2014xfa}
\\
\hline
\multirow{2}{*}{${B^+\to K^+ \bar\mu\mu}$}
    & \multirow{2}{*}{$\BR_\mu$}
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll} \\
    &
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014pli} \\
    & $A_{\rm FB}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa, CDF} \\
    & $F_{H}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline
    ${B^0\to K^{\ast 0} \bar\mu\mu}$
    & $\BR_\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline \hline
${B\to K}$ form factors
    & $f_{0,+,T}$   &  $q^2 = 17,\, 20,\, 23$ GeV$^2$  & \cite{Bouchard:2013eph} \\
\hline
\multirow{3}{*}{${B\to K^*}$ {form factors}}
    & $V/A_1$ &  $q^2 = 0$ GeV$^2$  & \cite{Hambrock:2013zya} \\
    & $A_0$   &  $q^2 = 0$ GeV$^2$  & \cite{Khodjamirian:2010vf} \\
    & $V$, $A_1$, $A_{12}$
              &  $q^2 = 15,\, 19.21$ GeV$^2$     & \cite{Horgan:2013hoa}  \\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:observables} List of all observables in the various
  exclusive $b\to s \bar\mu\mu$ decays that enter the fits with their
  respective kinematics and experiments that provide the measurements.
  Lattice results of $B\to K$ form factors are used to constrain their parameters,
  and theoretical constraints on $B\to K^*$ form factors are included. For
  more details see the text and \refapp{app:theory:inputs}.
}
\end{center}
\end{table*}

@@

Eventually we also explore the behaviour of derived constraints with respect
to destructive interference with vectorial couplings $\wilson{9,\,10}$. For
this purpose we include also the branching ratio \fred{and the rate CP asymmetry}
of $B\to K^* \bar\mu\mu$ as it provides additional constraints on the moduli
of vectorial couplings.

@@

As a matter of the fact there are no discrepancies between the latest measurements
for $\ell = \mu$ (throughout this section)
of $F_H^\mu$ and $A_{\rm FB}^\mu$ and their tiny SM predictions. Thus our main objective
is the derivation of stronger constraints on tensorial and scalar couplings, which
are enhanced in both observables compared to vectorial ones. For this purpose,
we will consider several model-independent scenarios, starting from rather
restricted to more general ones, in order to asses the effect of cancellations
among different contributions.

We will start with only tensorial couplings and see that they are well constrained
by $F_H^\mu$ alone. In a second step we consider only scalar couplings in order
to investigate the complementarity of $F_H^\mu$ and $B_s \to \bar\mu\mu$.
Eventually we will consider as a special scenario the SM augmented by dimension
six operators as an effective theory of new physics below some high scale
$\Lambda_{\rm NP}$, much larger than the typical scale of electroweak
symmetry breaking $v$ in the presence of one scalar doublet under $SU(2)_L$,
as in the SM, i.e. $v \ll \Lambda_{\rm NP}$.

>>>>

\begin{abstract}
  The angular distribution of $B\to K\bar\ell\ell$ ($\ell = e,\,\mu,\,\tau$)
  provides a lepton-forward-backward asymmetry $A_{\rm FB}^\ell$ and a flat
  term $F_H^\ell$ that are both suppressed in the standard model and very
  sensitive to nonstandard tensorial and scalar contributions. We use latest
  experimental results for $\ell = \mu$ in combination with $B_s\to \bar\mu\mu$
  to derive stronger model-independent constraints on tensorial and scalar
  effective couplings and determine their impact on $B\to K^*\bar\mu\mu$
  angular observables. Most notably, the measurement of $F_H^\mu$ provides
  constraints on (pseudo-)scalar couplings and their chirality-flipped
  counterparts that are complementary to the ones from the branching ratio
  $B_s\to \bar\mu\mu$, which allows to put for the first time simultaneously 
  upper bounds on all four couplings.
\end{abstract}

@@

Both observables, $F_H^\ell$ and $A_{\rm FB}^\ell$, exhibit strong suppression
factors for vectorial and dipole
couplings present in the SM, thereby enhancing their sensitivity to tensorial and
scalar couplings \cite{Bobeth:2007dw, Bobeth:2012vn}. A similar enhancement of
scalar couplings compared to helicity-suppressed vectorial couplings of the SM
is well-known from $B_s\to \bar\mu\mu$. Unfortunately the limited data set of
$B\to K^*(\to K\pi) \bar\ell\ell$ from LHCb \cite{Aaij:2013qta} still does not
allow to perform current angular analysis without the assumption of vanishing
scalar and tensorial couplings in this decay mode. In the future also certain
angular observables in $B\to K^* \bar\ell\ell$ will provide additional constraints
on such couplings, as for example $J_{6c}$ \cite{Altmannshofer:2008dz}
and the linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
\cite{Matias:2012xw, Bobeth:2012vn} as well as at low recoil the experimental
test of the relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 = 0$~\cite{Bobeth:2012vn}.

Here we exploit current data from $B^+\to K^+ \bar\mu\mu$ and $B_s\to \bar\mu\mu$
to derive stronger constraints then before on tensorial and scalar couplings in
various model-independent scenarios and study their impact on the yet not
measured analogous observables in $B\to K^* \bar\ell\ell$. In \refsec{sec:EFT},
we specify the effective theory of $|\Delta B| = 1$ decays, on which our
model-independent fits are based on. We discuss the dependence of observables
in $B\to K \bar\ell\ell$ and $B\to K^* \bar\ell\ell$ on the tensorial and scalar
couplings in \refsec{sec:observables} and specify also the experimental input
used in the fits. The constraints on tensorial and scalar couplings from the data
are presented for several model-independent scenarios in \refsec{sec:results}.
Technical details of the angular observables in $B\to K^* \bar\ell\ell$ and the
treatment of theory uncertainties are relegated to appendices.

@@

In the framework of the $|\Delta B| = |\Delta S| = 1$ effective theory
\begin{align}
  \label{eq:Heff}
  {\cal L}_{\rm eff} & =
   \frac{4 G_F}{\sqrt{2}} \,\frac{\alE}{4 \pi}\, V_{tb}^{} V_{ts}^\ast
       \sum_{\ell = e, \mu,\tau} \sum_i  \wilson[\ell]{i}(\mu_b)  \Op_i + \text{h.c.}
\end{align}
the most general dimension-six flavor-changing operators $\Op_i$ mediating
$b\to s \gamma$ and $b\to s \bar\ell\ell$ are classified according to their
chiral structure. There are dipole ($i = 7,7')$ and vectorial ($i = 9,9',10,10'$) 
operators
\begin{equation}
  \label{eq:SM:ops}
\begin{aligned}
  \Op_{7(7')} &
  = \frac{m_b}{e}\!\[\bar{s} \sigma^{\mu\nu} P_{R(L)} b\] F_{\mu\nu}\,,
\\
  \Op_{9(9')} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \ell\]\,,
\\[0.1cm]
  \Op_{10(10')} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
further scalar ($i = S,S',P,P'$) operators
\begin{equation}
  \label{eq:scalar:ops}
\begin{aligned}
  \Op_{S(S')} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \ell\]\,,
\\[0.1cm]
  \Op_{P(P')} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
and tensor ($i = T,T5$) operators
\begin{equation}
  \label{eq:tensor:ops}
\begin{aligned}
  \Op_{T} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \ell\]\,,
\\[0.1cm]
  \Op_{T5} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
where the notation $\Op_{T5} = i/2\, \varepsilon^{\mu\nu\alpha\beta}
\[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma_{\alpha\beta} \ell\]$ is
also used frequently in the literature. Their respective short-distance couplings,
the Wilson coefficients $\wilson[\ell]{i}(\mu_b)$ are evaluated at a scale of
the order of the $b$-quark mass $\mu_b \sim m_b$ and can be modified from SM
predictions in the presence of new physics.

The SM values $\wilson[\ell]{7,9,10}$ are obtained at next-to-next-to leading order
(NNLO) \cite{Bobeth:2003at, Huber:2005ig} and depend on the fundamental parameters
of the top-quark and $W$-boson masses, as well as on the sine of the weak mixing angle.
Moreover, they are universal for the three lepton flavors $\ell = e,\, \mu,\, \tau$.
All other Wilson coefficients are numerically suppressed or zero:
$\wilson[SM]{7'} = m_s/m_b\, \wilson[SM]{7}$, $\wilson[SM]{S,S',P,P'} \sim
{\cal O}(m_b^2/m_W^2)$, and $\wilson[SM]{9',10',T,T5} = 0$. Beyond the SM,
lepton-flavor non-universal effects are possible in principle and have been
discussed for example recently \cite{Alonso:2014csa, Hiller:2014yaa, Ghosh:2014awa,
Biswas:2014gga, Hurth:2014vma, Glashow:2014iga, Altmannshofer:2014rta, Hiller:2014abc} in
connection with the measurement of $R_K = {\cal B}_\mu/{\cal B}_e$ in
$q^2 \in [1, 6]$ GeV$^2$ \cite{Aaij:2014ora}, which deviates by $2.6\sigma$
from the SM prediction $R_K^{\rm SM} = 1.00$ \cite{Bobeth:2007dw, Bouchard:2013mia}.

@@

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensorial and scalar
couplings has been presented in \cite{Bobeth:2007dw, Bobeth:2012vn}, adopting
the effective theory \refeq{eq:Heff}, i.e. neglecting higher dimensional operators
with $\mbox{dim} > 6$. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}\,, &
  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests.
The $F_H^\ell(q^2)|_{\rm SM}$
is strongly suppressed away from both kinematical endpoints in $q^2$,
except for $\ell = \tau$, \cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.
Non-zero values
of $A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher order QED corrections,
which in principle could also give additional $\cos\theta_\ell$ dependence
to the angular distribution~\refeq{eq:ang-distr}, however, currently there is
no solid estimate available for this source of SM background.

@@

There are also angular observables $J_i$ in $B\to K^*(\to K\pi)\,
\bar\ell\ell$ with the same properties, i.e. tensorial and scalar contributions
are kinematically enhanced by a factor $\sqrt{q^2}/m_\ell$ over vectorial ones
present in the SM or their respective interference terms. These are $J_{6c}$
and the two linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
with explicit formulas given in \refapp{app:BKstarellell}.
In the limit of vanishing lepton mass one obtains that
\begin{align}
  J_{6c} & \propto
    \mbox{Re}\big[(\wilson[]{P} - \wilson[]{P'})\, \wilson[\ast]{T}
                - (\wilson[]{S} - \wilson[]{S'})\, \wilson[\ast]{T5}\big]
\intertext{is sensitive to the interference of tensorial and scalar operators,
  complementary to the $A_{\rm FB}^\ell$ in $B\to K \bar\ell\ell$}
  \label{eq:AFB-dependence}
  A_{\rm FB}^\ell & \propto
    \mbox{Re}\big[(\wilson[]{P} + \wilson[]{P'})\, \wilson[\ast]{T5}
                + (\wilson[]{S} + \wilson[]{S'})\, \wilson[\ast]{T}\big]
                \Big/ \Gamma_\ell \,,
\end{align}
i.e., with an interchange of tensorial contributions $T \leftrightarrow T5$.
We note also that $J_{6c}$ contributes to lepton forward-backward asymmetry
of $B\to K^* \bar\ell\ell$ being $\propto (J_{6s} + J_{6c}/2)$. Since
it has to compete with $J_{6s}$ in this observable, a separate measurement of
$J_{6s}$ and $J_{6c}$ is necessary. Further, only tensorial contributions enter
\begin{align}
  (J_{1s} - 3\, J_{2s}) & \propto
  \left(\ldots |\wilson{T}|^2 + \ldots |\wilson{T5}|^2 \right) \,,
\end{align}
where the dots indicate different kinematical and form factor dependences.
On the other hand, tensorial and scalar contributions enter
\begin{equation}
\begin{aligned}
  (J_{1c} + J_{2c}) & \propto
      \ldots \left(|\wilson{T}|^2 + |\wilson{T5}|^2 \right)
\\
  & + \ldots \left(|\wilson{S} - \wilson{S'}|^2 + |\wilson{P} - \wilson{P'}|^2 \right) \,,
\end{aligned}
\end{equation}
which is similar to the dependence of $F_H^\ell$ in $B\to K
\bar\ell\ell$
\begin{equation}
  \label{eq:FH-dependence}
\begin{aligned}
  F_H^\ell  \propto & \Big[
      \ldots \left(|\wilson{T}|^2 + |\wilson{T5}|^2\right)
\\
  & + \ldots \left(|\wilson{S} + \wilson{S'}|^2 + |\wilson{P} + \wilson{P'}|^2 \right)
  \Big]
  \Big/ \Gamma_\ell \,.
\end{aligned}
\end{equation}
Concerning $F_H^\ell$, the involved kinematical factors --- see \cite{Bobeth:2007dw,
Bobeth:2012vn} --- are such that tensorial and scalar couplings contribute only
constructively/cumulatively, apart of cancellations among $\wilson{S(P)}$ and $\wilson{S'(P')}$.
Further, interference terms (in the numerator of $F_H^\ell$) of $(\wilson{T} \times
\wilson{7,7',9,9'})$ and $(\wilson{P,P'} \times \wilson{10,10'})$ are suppressed
by $m_\ell/\sqrt{q^2}$, but can become relevant in case that $\wilson{T} \ll \wilson{7,7',9,9'}$
and $\wilson{P,P'} \ll\wilson{10,10'}$ can overcome this suppression factor,
respectively.

The observables $F_H^\ell$ \refeq{eq:FH-dependence} and $A_{\rm FB}^\ell$
\refeq{eq:AFB-dependence} are measured in the angular distribution \refeq{eq:ang-distr}
of $B\to K \bar\ell\ell$ being normalised to the decay width $\Gamma_\ell$, such
that uncertainties due to form factors can cancel in part \cite{Bobeth:2007dw, 
Bobeth:2012vn}. On the other hand, $J_{6c}$,  $(J_{1s} - 3\, J_{2s})$ and 
$(J_{1c} + J_{2c})$ appear in the unnormalised angular distribution of 
$B\to K^* \bar\ell\ell$ and so-called ``optimised'' versions $S_1$, $M_1$ and 
$M_2$ for the low-$q^2$ region have been identified in~\cite{Matias:2012xw}, 
respectively, where form factors cancel in the limit of $m_b \to \infty$. 
For the high-$q^2$ region potential normalisations are discussed in 
\refapp{app:BKstarellell}, which could serve to form optimised observables for
special scenarios of either vanishing chirality-flipped vectorial or tensorial
or scalar couplings. In the most general case, however, there are no optimised
observables at high-$q^2$. Although form factors do not cancel in this case, it
might be still advantageous to use normalisations, for example when the overall
normalisation of $B\to K^*$ form factors constitutes a major theoretical
uncertainty.

\begin{table*}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lccc}
\hline
Channel & Constraints & Kinematics & Source
\\
\hline \hline
$B_s\to \bar\mu\mu$
& $\int\dd\tau \BR(\tau)$ &  --  & \cite{Aaij:2013aka,Chatrchyan:2013bka,CMS:2014xfa}
\\
\hline
\multirow{2}{*}{${B^+\to K^+ \bar\mu\mu}$}
    & \multirow{2}{*}{$\BR_\mu$}
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll} \\
    &
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014pli} \\
    & $A_{\rm FB}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa, CDF} \\
    & $F_{H}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline
    ${B^0\to K^{\ast 0} \bar\mu\mu}$
    & $\BR_\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline \hline
${B\to K}$ form factors
    & $f_{0,+,T}$   &  $q^2 = 17,\, 20,\, 23$ GeV$^2$  & \cite{Bouchard:2013eph} \\
\hline
\multirow{3}{*}{${B\to K^*}$ {form factors}}
    & $V/A_1$ &  $q^2 = 0$ GeV$^2$  & \cite{Hambrock:2013zya} \\
    & $A_0$   &  $q^2 = 0$ GeV$^2$  & \cite{Khodjamirian:2010vf} \\
    & $V$, $A_1$, $A_{12}$
              &  $q^2 = 15,\, 19.21$ GeV$^2$     & \cite{Horgan:2013hoa}  \\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:observables} List of all observables in the various
  exclusive $b\to s \bar\mu\mu$ decays that enter the fits with their
  respective kinematics and experiments that provide the measurements.
  Lattice results of $B\to K$ form factors are used to constrain parameters
  of their $q^2$-dependence,
  and theoretical constraints on $B\to K^*$ form factors are included. For
  more details see the text and \refapp{app:theory:inputs}.
}
\end{center}
\end{table*}

@@

Eventually we also explore the behaviour of derived constraints with respect
to destructive interference with vectorial couplings $\wilson{9,\,10}$. For
this purpose we include also the branching ratio \fred{and the rate CP asymmetry}
of $B\to K^* \bar\mu\mu$ as it can provide additional constraints on the 
imaginary parts of vectorial couplings.

@@

As a matter of the fact there are no discrepancies between the latest measurements
for $\ell = \mu$ (throughout this section) of $F_H^\mu$ and $A_{\rm FB}^\mu$ and
their tiny SM predictions. Thus our main objective is the derivation of stronger
constraints on tensorial and scalar couplings, taking advantage of their enhancement
in both observables over vectorial ones. For this purpose, we will consider several
model-independent scenarios, starting from rather restricted to more general ones,
in order to asses the effect of cancellations due to interference of various
contributions.
